\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to express my deep gratitude to the Ministry of Education, Culture, Sports, Science and Technology of Japan for allowing me to pursue my Master's studies by proving me with a scholarship.

To Professor Kenichi Matsumoto for giving me the opportunity of been a part of his research laboratory, and for all the support provided inside and outside the university. He was always very kind and despite having a very tight schedule He was always available.

I would also like to thank professor Akinori Ihara for the support he gave throughout my research. He always motivated me to keep pushing forward and getting more ideas.

I am particularly grateful for the assistance given by my supervisor, professor Raula Kula for the continuous discussions and feedback provided during my Master's studies and the execution of this thesis. He was a great support not only in the academic but also in the personal aspect.

I would like to thank Rakuten Company for giving me the opportunity to start a professional life in Japan after my graduation and for all the support given during my internship and part-time job.

I would like to offer my special thanks to Tomohiko Sato for been a great support in various aspects, making my life in Japan fulfilling and rich.

There are so many people I would like to thank, that I wouldn't be able to mention all of them. My Host Family, Friends, Japanese Language volunteer teachers and many more that had aid me during my time in Japan. To all of them that had made feel part of this community despite being from a foreign country.


And finally, I cannot express my gratitude for having a wonderful family, for all the sacrifices they have done and for all the support they have provided me to be able to fulfill my dreams.
\enlargethispage{\baselineskip}